Supporting Information: Unsupervised embedding of trajectories captures the latent structure of mobility

### 2021-02-19 paper/current/supp.tex
\cite to \autocite in supp

We also consider Laplacian eigenmaps \cite{belkin2003laplacian}, which is the most fundamental graph embedding method, as the second benchmark on the matrix factorization. First, we construct the co-occurrence matrix of $N$ organization, $A_{ij}$ given by the co-occurence of $i$ and $j$ in the same affiliation trajectory and degree matrix $D$ which is the diagonal matrix for which $D_{ii}=\sum_j {A_{ij}}$. Then we construct graph lapalcian matrix $L = D-A$  and apply  truncated singular vector decomposition in the matrix $L$ with $d=300$.

@@

Furthermore, We examine the gravity model with embedding vector with the symmetric SVD  \textit{word2vec} method\cite{levy2014neural} as the third benchmark on the matrix factorization. Based on idea of \textit{word2vec} is just implciity matrix factorization, Levy proposed symmetric SVD \textit{word2vec} embedding. First, we construct the matrix of $N$ organization,

>>>>

We also consider Laplacian eigenmaps \autocite{belkin2003laplacian}, which is the most fundamental graph embedding method, as the second benchmark on the matrix factorization. First, we construct the co-occurrence matrix of $N$ organization, $A_{ij}$ given by the co-occurence of $i$ and $j$ in the same affiliation trajectory and degree matrix $D$ which is the diagonal matrix for which $D_{ii}=\sum_j {A_{ij}}$. Then we construct graph lapalcian matrix $L = D-A$  and apply  truncated singular vector decomposition in the matrix $L$ with $d=300$.

@@

Furthermore, We examine the gravity model with embedding vector with the symmetric SVD  \textit{word2vec} method\autocite{levy2014neural} as the third benchmark on the matrix factorization. Based on idea of \textit{word2vec} is just implciity matrix factorization, Levy proposed symmetric SVD \textit{word2vec} embedding. First, we construct the matrix of $N$ organization,
